### 2016-06-09 paper/evaluation.tex
More comments while reading

\input{fig_examples-required-table}
As we see in Figure~\ref{fig:examples-required-table}, examples are not too
important for synthesizing bijective lenses.
Because bijective lenses have very few well typed programs, compared to the
number of functions, oftentimes just a few examples is sufficient.
As would be expected, the functions that have to make choices about the
locations of where data goes are those that require more examples.
In particular, the address problem requires more examples, because it must make
choices of where information goes, like which name is the a person's first name,
and which is their last.

>>>>

\input{fig_examples-required-table}
As we see in Figure~\ref{fig:examples-required-table}, examples are not too
important for synthesizing bijective lenses.\bcp{If that's really the
  conclusion, then maybe we should have written a paper about synthesizing
  bijective lenses {\em without} examples!  But I don't think we can
  actually conclude this from the examples we have.  }
Because bijective lenses have very few well typed programs, compared to the
number of functions, oftentimes just a few examples is sufficient.
As would be expected, the functions that have to make choices about the
locations of where data goes are those that require more examples.
In particular, the address problem requires more examples, because it must make
choices of where information goes, like which name is the a person's first name,
and which is their last.
